Deep Learning

### 2015-01-12 deepreview.tex
added RNN figure and caption

\begin{figure}[H]
\centerline{
\includegraphics[width=0.49\linewidth]{bp-mlp1.pdf}
\includegraphics[width=0.49\linewidth]{bp-mlp5.pdf}
}
\caption{Top left: graph of feedforward computations in a multi-layer
neural network with one input layer ($x$), two hidden layers ($h_1$ and $h_2$),
one output layer (out), a target $y$, and an error that compares the output
and the target. The synaptic weight matrices $W_1$, $W_2$ and $W_3$ are
the parameters of the neural network.\newline
Top right: back-propagation through the same multi-layer neural network
(downward arrows compute the partial derivative of the error with respect
to every node, i.e., the units value and the parameters.\newline
Bottom:
}
\label{fig:mlp}
\end{figure}

>>>>

\begin{figure}[H]
\centerline{
\includegraphics[width=0.49\linewidth]{bp-mlp1.pdf}
\includegraphics[width=0.49\linewidth]{bp-mlp5.pdf}
}
\centerline{
\includegraphics[width=0.89\linewidth]{fig-hidden-recurrence-rnn.pdf}
}
\caption{Top left: graph of feedforward computations in a multi-layer
neural network with one input layer ($x$), two hidden layers ($h_1$ and $h_2$),
one output layer (out), a target $y$, and an error that compares the output
and the target. The synaptic weight matrices $W_1$, $W_2$ and $W_3$ are
the parameters of the neural network.\newline
Top right: back-propagation through the same multi-layer neural network
(downward arrows compute the partial derivative of the error with respect
to every node, i.e., the units value and the parameters).\newline
Bottom: a recurrent neural network (left) and the unfolding in time of the
computation involved in its forward computation. The artificial neurons
(e.g. hidden units grouped under node $s$ with values $s_t$ at time $t$) 
get inputs from other neurons at previous time steps
(this is represented with the black square, for delay of
one time step, on the left). In this way, a recurrent net can map an input sequence
with elements $x_t$ into an output sequence with elements $o_t$, with
each $o_t$ depending on all the previous $x_{t'}$ (for $t'\leq t$). The
same parameters (matrices $U$, $V$, $W$) are used at each time step.
Many other architectures are possible, including a variant in which
the outputs (e.g. words) can be generated according to a distribution 
(the probability of the next word) and used as inputs for the next time step.
The back-propagation algorithm (Figure~\ref{fig:backprop-box})
can be directly applied to the computational graph of the unfolded network
on the right hand side, to compute the derivative of a total error
(at all time steps) with respect to all the states $s_t$ and all the parameters.
}
\label{fig:mlp}
\end{figure}
